### 2010-02-11 docs/architecture/architecture.tex
some additions from a while back that were never checked in

@@

@@

>>>>

\subsection{{\tt eos\_module}}

@@

\subsection{{\tt network}}

@@

\subsection{Amrvis}

\subsection{{\tt data\_processing} scripts}

Several useful analysis scripts can be found in {\tt
fParallel/data\_processing}.  The makefile there needs
to be edited to indicate which of the tools to build.

\item {\tt fextract3d}

  Extracts a 1-d slice from a plotfile, through the center of the
  domain in any coordinate direction.  Either all of the variables or
  a single variable is output.

\item {\tt fextrema}

  Outputs the min/max of each of the quantities in the plotfile.

\item {\tt ftime}

  Outputs the simulation time for one or more plotfiles.

\subsection{VisIt}
